---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# fmp: An R package for interfacing with the Financial Modeling Prep API 

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/fmp)](https://CRAN.R-project.org/package=fmp)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

The goal of `fmp` is to provide a simple and consistent interface to the **Financial Modeling Prep** [Financial Data API](https://financialmodelingprep.com/) that can be used along side and integrated with other common R resources 
for collecting and analyzing financial data, such as `tidyquant`, `xts`, `TTR`, and `quantmod`.

## Installation

<!-- You can install the released version of fmp from [CRAN](https://CRAN.R-project.org) with: -->
<!-- --- actually not on CRAN yet -->
<!-- ``` r -->
<!-- install.packages("fmp") -->
<!-- ``` -->
You can install the latest development version of fmp from [Github](https://github.com) with:

``` r
remotes::install_github('jpiburn/fmp')
```

## Getting Started

Before getting started with `fmp` you first must obtain an API key for the Financial Modeling Prep Financial Data API. For details, see [here](https://financialmodelingprep.com/developer/docs/pricing/).

Once you sign up, you can add your API key to your `.Renviron` file by using `fmp_api_key()`. This will add a `FMP_API_KEY` entry to your `.Renviron` file so it will automatically be available in future sessions. When first installed however, you will need to reload your .Renviron file by either restarting R or running `readRenviron('~/.Renviron')`

```{r api-key, eval=FALSE}
library(fmp)

api_key <- 'my_api_key'
fmp_api_key(api_key)

# reload
readRenviron('~/.Renviron')
```

## Company Valuation
The Financial Modeling Prep Financial Data API, provides several useful enpoints for company valutation analysis.From general company overviews, using `fmp_profile()`

```{r ex-profile}
library(dplyr)
library(fmp)

my_stocks <- c('AAPL', 'GE')

d <- fmp_profile(my_stocks)

glimpse(d)
```

To more detailed analysis, such as cash flow and balance sheet statements, key metrics, and discounted cash flow value.
```{r ex-detailed}
library(dplyr)
library(fmp)

my_stocks <- c('AAPL', 'GE')

d_cash <- fmp_cash_flow(my_stocks)
d_balance <- fmp_balance_sheet(my_stocks)
d_metrics <- fmp_key_metrics(my_stocks)

glimpse(d_metrics)
```

## More documentation coming soon
